Summary

### 2015-10-29 inst/examples/summary.Rmd
ok

library(stringr)
library(dplyr)
library(ggplot2)
ntop <- 20

@@

[Discarded page count data](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/documentpages-accepted-discarded.csv)

[Successfully converted page counts](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/documentpages-accepted.csv)

>>>>

library(stringr)
library(dplyr)
library(reshape2)
library(ggplot2)
ntop <- 20

@@

[Discarded page count data](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/documentpages_discarded.csv)

[Successfully converted page counts](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/documentpages_accepted.csv)
